\Large\textbf{Decentralized Data Marketplace to Enable Trusted Machine Economy}

### 2019-09-09 paper.tex

Data provider would receive subscription fee for buying data each time the data is transmitted to consumer; unpaid subscription fee would be stored in smart contract. The consumer will keep buying data from data povider, only when the data sold by the data provider with high enough accuracy, which we called these data as decent data.
Once the accuracy is lower than a certain accuracy, which we called it as unacceptable data, the consumers would consider this data provider as a low quality data provider, and reject to buy the data from this data provider.

@@

\subsection{Game Theory Evaluation}
\subsubsection{Repeated Game}
Repeated game consists of serveral repetitions of some stage games. In each stage game, the action player takes will effect the actions that players are going to take in the future stages. Repeated game can be illustrated with a decision tree and described their payoff with discounted sum of payoff. Discounted sum of payoff can capture the idea that what the players truly pursue is the sum of payoff in all stages and payoff in different stages may varify.

\subsubsection{Model Description}
We use a repeated game to express the scenario of our Data Marketplace. Figure.\ref{fig:decision_tree} shows the decision tree to depict the the repeated game we used. Each level in this decision tree represents each round of data transmission from data provider to consumers, and the consumers would pay subscription fee, $p_s$, each person. The sum of all the subscription fee pays to data provider is denoted as $P_s$.

Refund is a major issue in our research. However, we don't have to take refund as a factor in our repeated game, since in our decentralized data marketplace we use smart contract to store the subscription fee which will be paid to buy the future data. The subscription fee will be paid as data provider provides new data. In other words, data provide doesn't need to take any procedure to transer subscription fee from his/her own account to consumers' account. For the same reason, data provider has no responsibility on the refunding processing fee charged by the smart contract as well.

@@

We have these following assumptions:
\begin{itemize}
    \item  There is no any other data providers provide the same product in Data Marketplace. Therefore, we can consider each provider's behavior independently. That means this decision tree represent the behavior of only one data provider.
    \item  More than 51\% of consumers are among complete information exchange state. In other words, once one of them launches voting for stopping buying data and refunding, they would succeed in refund voting.
    \item  One of the consumers who has complete information exchange with other 51\% buyers has the ability to examine the data quality. If unacceptably low accuracy data are delivered to consumers, this examiner will spread this information out.
\end{itemize}

@@

\begin{itemize}
    \item $P_s$ is the sum of subscription price (fee) for all subscriber.
    \item $C_{maintain}$ is the cost of sensor maintenance in $n$ round.
    \item $\beta$ is discounted factor.
    \item $n$ is how many round for one maintenance period.
    \item $m$ is how many maintenance periods have been experienced in this repeated game.
\end{itemize}

>>>>

The consumer will pay for the data, only when the data sold by the data provider with high enough quality/accuracy, which we called these data as decent data.
Once the accuracy is lower than a certain threshold, which we called these data as unacceptable data, the consumers would consider this data provider as a low quality data provider, and stop buying data from this data provider.

Refund is a major issue in our research. However, we don't have to take refund as a factor in our game theory model, since in our decentralized data marketplace we use smart contract to store the subscription fee which will be paid to buy the future data. The subscription fee will be paid as new data is transmitted to consumers. In other words, data provider doesn't need to take any procedure to transfer subscription fee from his/her own account to consumers' account. For the same reason, data provider has no responsibility on the refunding processing fee charged by the smart contract as well.

@@

\subsection{Game Theory Evaluation}
Game Theory is a methodology to discuss strategic interaciton among game players. If we can ensure Nash Equilibrium of decentralized data marketplace exists at certain acceptable range, then we can promise the sustainability of decentralized data marketplace. Fan Liang et al\cite{SurveyBigDataPricing} listed several different types of game theory models which are applied on data pricing. To describe the scenario more precisely, we decided to use repeated game to build our game theory model which meets the scenario of subscription economy more.

Figure.\ref{fig:decision_tree} shows the decision tree to depict the the repeated game we used. Each level in this decision tree represents each round of data transmission from data provider to consumers, and the consumers would pay subscription fee, $p_s$, each person. The sum of all the subscription fee pays to data provider is denoted as $P_s$.

@@

We have these following assumptions:
\begin{itemize}
    \item  There is no any other data providers provide the same product in Data Marketplace. Therefore, we can consider each provider's behavior independently. That means this decision tree represent the behavior of only one data provider.
    \item  More than 51\% of consumers are among complete information exchange state. In other words, once one of them launches voting for stopping buying data and refunding, they would succeed in refund voting.
    \item  One of the consumers who has complete information exchange with other 51\% buyers has the ability to examine the data quality. If unacceptably low accuracy data are delivered to consumers, this examiner will spread this information out.
    \item  We assume the number of dishonest consumers is really small, so it can be negleted.
\end{itemize}

@@
